A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-21 paper.tex
2d chiral edits

@@

We begin with a description of certain pure supersymmetric Yang--Mills theories. Let $V_\RR = \RR^n$ be a real vector space of dimension $n$ equipped with a nondegenerate symmetric bilinear pairing and let $V$ be its complexification. 
Fix a $\ZZ/2\ZZ$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
\[\Gamma\colon \Sym^2(\Sigma)\rightarrow V,\qquad \Gamma\colon \Sym^2(\Sigma^*)\rightarrow V\]
defined as in Appendix \ref{sect:spinors}. We make the following assumption on this setup.

@@

Denote by $F_A = \d A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd\d_A$ be the twisted Dirac operator obtained from $\Gamma$ (see Appendix \ref{sect:spinors}).

@@

We turn to $\cN=(2,0)$ supersymmetric Yang-Mills theory.
In the supersymmetry algebra, we have $W_-=0$ and $W_+$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
The supersymmetric matter consists of the $\cN = (2,0)$ chiral multiplet with values in a representation $R$. 
The $R$-symmetry group is $G_R = \SO(2;\CC)$ which acts on $W_+$ by the defining representation.

The fields of the untwisted theory are:
\begin{itemize}
\item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_+ \otimes W_+ \otimes \fg)$. 
\item matter bosons $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
\item matter fermions $\psi \in C^\infty(\RR^2 ; S_- \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_- \otimes R)$.
\item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
\end{itemize}
The field $\lambda$ transforms in the defining representation of $G_R = \SO(2;\CC)$.
The fields $\psi, \Bar{\psi}$ have weights $-1,+1$ respectively.

The theory admits a unique twist by the following class of supercharge.
\begin{itemize}
\item Elements $Q \in S_+ \otimes W_+$ of rank $1$. 
Such supercharges are automatically square-zero and are holomorphic.
We take $\alpha \colon U(1) \hookrightarrow G_R$ to be the standard embedding.
There is a compatible twisting homomorphism
\[
\phi \colon \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R .
\]
\end{itemize}

\subsubsection{Minimal Twist} \label{sect:2d20minimaltwist}

Choose a complex structure $L \subset V_\RR$. 
Under the embedding $U(1) \hookrightarrow \spin(2;\CC)$, the semi-spin representations decompose as
\[
S_+ = \det(L)^{1/2} \;\; , \;\; S_- = \det(L)^{-1/2} .
\]

@@

\begin{theorem} \label{thm:2d(2,0)}
The minimal twist of 2d $\cN=(2,0)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
This equivalence is $\U(1)$-equivariant.
\end{theorem}
\begin{proof}
%The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int (\phi, \psi_0^*)$.  
Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
which can be integrated out using Proposition \ref{prop:BRSTdoublet}.

@@

Next, we consider $\cN=(4,0)$ supersymmetric Yang-Mills theory.
In the supersymmetry algebra, we have $W_- = 0$ and $W_+$ is a complex four-dimensional vector space equipped with a nondegenerate symmetric bilinear pairing.
The supersymmetric matter consists of the $\cN = (4,0)$ hypermultiplet with values in a complex symplectic representation $U$. 
The $R$-symmetry group is $G_R = \SL(2;\CC) \times \GL(1;\CC)$.
As a $G_R$-representation, $W_+ = \Tilde{W} \oplus \Tilde{W}$ where $\Tilde{W}$ is the defining representation of $\SL(2;\CC)$ and where $\GL(1;\CC)$ acts by weight $(1,-1)$ with respect to this decomposition.

@@

\subsubsection{Minimal twist} \label{sect:2d40minimaltwist}

Choose a complex structure $L \subset V_\RR$. 
Under the embedding $U(1) \hookrightarrow \spin(2;\CC)$, the semi-spin representations decompose as
\[
S_+ = \det(L)^{1/2} \;\; , \;\; S_- = \det(L)^{-1/2} .
\]
We choose a twisting homomorphism $\phi : \U(1) \to G_R$ under which $\Tilde{W} = \det(L)^{1/2} \oplus \det(L)^{-1/2}$
so that
\[
S_+ \otimes W_+ = \CC Q \oplus \CC \oplus L^{\oplus 2} .
\]

The twisting data homomorphism is the natural embedding $\alpha \colon \U(1) \hookrightarrow \GL(1;\CC) \to G_R$.

@@

\begin{theorem} \label{thm:2d(4,0)}
The minimal twist of 2d $\cN=(4,0)$ super Yang-Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
This equivalence is $\U(1)$-equivariant.
\end{theorem}

\begin{proof}
First, we integrate out the field $\lambda^-$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the terms $\int  (\lambda^-_{1,0} , A_{1,0}^*)$ and  $\int (\psi_-, \nu^*)$.  
Thus, the two pairs $(\lambda^-_{1,0}, A_{1,0})$ and $(\nu, \psi_-)$ form BRST doublets, 
which can be integrated out using Proposition \ref{prop:BRSTdoublet}.

@@

We consider pure $\cN=(\cN_+,0)$ super Yang-Mills for a Lie algebra $\fg$, where $\cN_+ \geq 2$.
The spinorial representation is $\Sigma = S_+ \otimes W_+$ where $W_+$ is the $\cN_+$-dimensional auxiliary equipped with a nondegenerate symmetric bilinear pairing.

@@

\subsubsection{Minimal Twist} \label{sect:2dN0minimaltwist}

Choose a complex structure $L \subset V_\RR$. 
Under the embedding $U(1) \hookrightarrow \spin(2;\CC)$, the semi-spin representations decompose as
\[
S_+ = \det(L)^{1/2} \;\; , \;\; S_- = \det(L)^{-1/2} .
\]

@@

\begin{theorem} \label{thm:2d(N,0)}
The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
This equivalence is $\U(1)$-equivariant.
\end{theorem}

\begin{proof}
%The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the term $\int  (\lambda_{1,0} , A_{1,0}^*)$.
Thus, the pair $(\lambda_{1,0}, A_{1,0})$ forms a BRST doublet, 
which can be integrated out using Proposition \ref{prop:BRSTdoublet}.

@@

\appendix

\section{Spinors}
\label{sect:spinors}

>>>>

\subsection{Spinors}
\label{sect:spinors}

@@

We begin with a description of certain pure supersymmetric Yang--Mills theories. Let $V_\RR = \RR^n$ be a real vector space of dimension $n$ equipped with a nondegenerate symmetric bilinear pairing and let $V$ be its complexification. 
Fix a $\ZZ/2\ZZ$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
\[\Gamma\colon \Sym^2(\Sigma)\rightarrow V,\qquad \Gamma\colon \Sym^2(\Sigma^*)\rightarrow V\]
defined as in Section \ref{sect:spinors}. We make the following assumption on this setup.

@@

Denote by $F_A = \d A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd\d_A$ be the twisted Dirac operator obtained from $\Gamma$ (see Section \ref{sect:spinors}).

@@

We turn to the $\cN=(2,0)$ supersymmetric Yang-Mills theory.
In the supersymmetry algebra, we have $W_-=0$ and $W_+$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
The supersymmetric matter consists of the $\cN = (2,0)$ chiral multiplet with values in a $\fg$-representation $R$. 
The R-symmetry group is $G_R = \SO(2;\CC)$ which acts on $W_+$ by the defining representation.

The fields of the untwisted theory are:
\begin{itemize}
\item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
\item gauge fermions $\lambda \in C^\infty(\RR^2 ; \Pi S_+ \otimes W_+ \otimes \fg)$. 
\item matter bosons $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
\item matter fermions $\psi \in C^\infty(\RR^2 ; \Pi S_- \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; \Pi S_- \otimes R)$.
\item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
\end{itemize}
The field $\lambda$ transforms in the defining representation of $G_R = \SO(2;\CC)$.
The fields $\psi, \Bar{\psi}$ have weights $-1,+1$ respectively.

The theory admits a unique twist by the following class of supercharge.
\begin{itemize}
\item Elements $Q \in S_+ \otimes W_+$ of rank $1$. 
Such supercharges are automatically square-zero and are holomorphic.
We take $\alpha \colon U(1) \hookrightarrow G_R$ to be the standard embedding.
There is a compatible twisting homomorphism
\[
\phi \colon \MU(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R .
\]
\end{itemize}

\subsubsection{Holomorphic Twist} \label{sect:2d20minimaltwist}

Choose a complex structure $L \subset V$. 
Under the embedding $MU(1) \hookrightarrow \Spin(2; \CC)$, the semi-spin representations decompose as
\[
S_+ = \det(L)^{1/2} \;\; , \;\; S_- = \det(L)^{-1/2} .
\]

@@

\begin{theorem} \label{thm:2d(2,0)}
The holomorphic twist of the 2d $\cN=(2,0)$ super Yang--Mills theory with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to the holomorphic $BF$ theory with the space of fields $T^*[-1] \map(\CC , R / \fg)$.
This equivalence is $\U(1)$-equivariant.
\end{theorem}
\begin{proof}
%The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
First, we eliminate the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int (\phi, \psi_0^*)$.  
Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
which can be eliminated using Proposition \ref{prop:BRSTdoublet}.

@@

Next, we consider the $\cN=(4,0)$ supersymmetric Yang--Mills theory.
In the supersymmetry algebra, we have $W_- = 0$ and $W_+$ is a complex four-dimensional vector space equipped with a nondegenerate symmetric bilinear pairing.
The supersymmetric matter consists of the $\cN = (4,0)$ hypermultiplet with values in a complex symplectic $\fg$-representation $U$. 
The R-symmetry group is $G_R = \SL(2;\CC) \times \GL(1;\CC)$.
As a $G_R$-representation, $W_+ = \Tilde{W} \oplus \Tilde{W}$ where $\Tilde{W}$ is the defining representation of $\SL(2;\CC)$ and where $\GL(1;\CC)$ acts by weight $(1,-1)$ with respect to this decomposition.

@@

\subsubsection{Holomorphic twist} \label{sect:2d40minimaltwist}

Choose a complex structure $L \subset V$. 
Under the embedding $MU(1) \hookrightarrow \Spin(2; \CC)$, the semi-spin representations decompose as
\[
S_+ = \det(L)^{1/2} \;\; , \;\; S_- = \det(L)^{-1/2} .
\]
We choose a twisting homomorphism $\phi\colon \U(1) \to G_R$ under which $\Tilde{W} = \det(L)^{1/2} \oplus \det(L)^{-1/2}$
so that
\[
S_+ \otimes W_+ = \CC Q \oplus \CC \oplus L^{\oplus 2} .
\]

The $\ZZ$-grading is induced by a natural embedding $\alpha \colon \U(1) \hookrightarrow \GL(1;\CC) \to G_R$.

@@

\begin{theorem} \label{thm:2d(4,0)}
The holomorphic twist of the 2d $\cN=(4,0)$ super Yang--Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with the space of fields $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
This equivalence is $\U(1)$-equivariant.
\end{theorem}

\begin{proof}
First, we eliminate the field $\lambda^-$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the terms $\int  (\lambda^-_{1,0} , A_{1,0}^*)$ and  $\int (\psi_-, \nu^*)$.  
Thus, the two pairs $(\lambda^-_{1,0}, A_{1,0})$ and $(\nu, \psi_-)$ form BRST doublets, 
which can be eliminated using Proposition \ref{prop:BRSTdoublet}.

@@

We consider pure $\cN=(\cN_+,0)$ super Yang-Mills for a Lie algebra $\fg$, where $\cN_+ \geq 2$.
The spinorial representation is $\Sigma = S_+ \otimes W_+$ where $W_+$ is the $\cN_+$-dimensional auxiliary space equipped with a nondegenerate symmetric bilinear pairing.

@@

\subsubsection{Holomorphic Twist} \label{sect:2dN0minimaltwist}

Choose a complex structure $L \subset V$. 
Under the embedding $U(1) \hookrightarrow \spin(2;\CC)$, the semi-spin representations decompose as
\[
S_+ = \det(L)^{1/2} \;\; , \;\; S_- = \det(L)^{-1/2} .
\]

@@

\begin{theorem} \label{thm:2d(N,0)}
The holomorphic twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to the holomorphic $BF$ theory with the space of fields $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
This equivalence is $\U(1)$-equivariant.
\end{theorem}

\begin{proof}
%The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
First, we eliminate the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the term $\int  (\lambda_{1,0} , A_{1,0}^*)$.
Thus, the pair $(\lambda_{1,0}, A_{1,0})$ forms a BRST doublet, 
which can be eliminated using Proposition \ref{prop:BRSTdoublet}.

@@
